% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2010 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
	\textbf{\large Brendan T. Heussler}  & 410.980.9672 (cell)\\
	850 Holly Dr &  bheussler@gmail.com \\
	Annapolis, MD  21409\\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
	\item
	\ressubheading{Connecticut College}{New London, CT}{B.A. Major Computer Science, Minor Economics (\textbf{GPA 3.28})}{Aug. 2008 - May. 2012}
	\begin{itemize}
		\resitem{Senior Research: Genetic Algorithms Applied to Economic Contagion}
		\resitem{Relevant Courses: Computational Intelligence, Artificial Intelligence, Networks, Algorithms, Data Structures, Computer Organization, Topics in Software Development}
	\end{itemize}
	
	\item
	\ressubheading{University of Nottingham}{Nottingham, UK}{Study Abroad}{Sept. 2010 - Jan. 2011}
	\begin{itemize}
		\resitem{Relevant Courses: Operations Research and Optimization, Knowledge Representation and Reasoning, Graphical User Interfaces, Software Engineering Methodologies, Introduction to Formal Reasoning}
	\end{itemize}
\end{itemize}

\resheading{Work Experience}
\begin{itemize}
	\item
	\ressubheading{iNovex Information Systems}{Annapolis, MD}{Intern}{May 2011 - Aug. 2011}
	\begin{itemize}
		\resitem{Linked public databases with information on registered sex offenders}
		\resitem{Developed Semantic Web Technology built to W3C specifications}
		\resitem{Converted data stored in MySQL databases to linked data (RDF)}
		\resitem{Built ontology for sex offenders that extends existing ontologies}
		\resitem{Created and connected several SPARQL endpoints}
	\end{itemize}
\end{itemize}

\resheading{School Projects}
\begin{itemize}
	\item
	\ressubheading{Various AI Algorithms}{Connecticut College}{Artificial Intelligence, COM 316}{Sept. 2011 - Dec. 2011}
	\begin{itemize}
		\resitem{Built goal finding robots that used popular search techniques}
		\resitem{Modeled propositional and first order logic applied to a search space}
		\resitem{Learned other important topics including learning and connectionist systems}
	\end{itemize}
	
	\item
	\ressubheading{Visual Data Structures}{}{Algorithms, COM 304}{Jan. 2011 - May 2011}
	\begin{itemize}
		\resitem{Created GUI representations of a Binomial Heap and a Disjoint Set}
		\resitem{Used Java to program Model-View-Controller architecture}
	\end{itemize}

	\item
	\ressubheading{Web Browser}{University of Nottingham}{Graphical User Interfaces, G52GUI}{Sept. 2010 - Jan 2011}
	\begin{itemize}
		\resitem{Developed simple web browser with Swing Java}
		\resitem{Incorporated Agile development methodologies}
	\end{itemize}
\end{itemize}

\resheading{Skills}
\begin{description}
	\item[Languages:]
		Java, Python, Perl, SQL, Scheme, \LaTeX
	\item[Operating Systems:]
		Linux (Debian), Mac OS X, {\sc UNIX}, Windows XP/Vista/7, Solaris
	\item[Applications:]
		Eclipse, Maven, Subversion, Git, Scheme Widget Library, Microsoft Excel
\end{description}




\end{document}
